Blocking-resistant communication\\through domain fronting

### 2015-02-13 docs/fronting.tex
New Psiphon clients data.
Generate bandwidth-lantern graph.
Trimming Lantern content

Lantern~\cite{lantern} is a free circumvention tool targeting casual web browsing.
Lantern does not employ onion routing and in general does not provide the
same level of anonymity guarantees as Tor.  Lantern primarily focuses on
performance and availability.

At its core, Lantern is a network of shared HTTPS proxy servers combined
with a client application that allows censored users to find and use those
proxy servers to proxy traffic from their existing web browsers.  This same
client application also allows uncensored users to host such proxy servers
on their own networks for use by other Lantern users. Lantern ultimately
aims to provide a secure mechanism for distributing knowledge about both
Lantern-hosted and peer-hosted proxy servers using a trust-network based
distribution mechanism such as kaleidoscope~\cite{kaleidoscope}.  In the meantime, Lantern
also randomly assigns users to Lantern-hosted proxy servers.

Lantern uses a centralized infrastructure for authenticating users and
assigning proxies to them.  Lantern's threat model assumes that this
centralized infrastructure is or can be blocked by the censors.
Consequently, users must have a priori access to a functioning proxy which
they can use to bootstrap onto the Lantern network and learn about more
proxies. Prior to Lantern adopting domain-fronting, we gave users access to
such proxies (which we call fallbacks) by embedding their information in
customized software installers that we distributed directly to users.  This
prevented users from downloading Lantern directly and required them to
request an email invitation from us with a link to their custom installer.
Furthermore, since anyone could request an installer, the censors could
theoretically learn about all of our proxies simply by continually
requesting installers.

\subsection{Timeline for Deploying Domain-Fronting}

\begin{figure}
\centering
\includegraphics[height=1.5in]{clients-lantern}
\caption{
Megabytes per second served by domain-fronted Lantern proxies
(Lantern-hosted and peers).
}
\label{fig:lantern-bandwidth}
\end{figure}

Lantern rolled out domain-fronting via CloudFlare in July 2014 in order to
allow users to direct-download Lantern without an email invitation.  In
this initial implementation, direct-downloaded Lantern clients proxied all
their traffic using domain-fronting.  It worked, and we experienced steady
growth in direct downloads and traffic from direct-downloaded clients.

At the beginning of October 2014, we started randomly assigning direct
HTTPS proxies to users who had direct-downloaded Lantern.  This diverted
traffic from domain-fronted servers to more efficient direct servers.

In December 2014 and January 2015, Lantern experienced a dramatic surge in
domain-fronted traffic, jumping from 1 MB/s to 100 MB/s within those two
months. At first we assumed that direct proxies had been blocked, but it
turns out that the majority of this new traffic originated in the
Philippines, which is not a heavily censored country. From what we're
hearing, it looks like Philippine users are using Lantern to get around
their ISPs bandwidth caps~\cite{needed}.

\subsection{General Deployment Considerations}

Unlike with meek, Lantern's equivalent of reflectors (which we call
proxies) are also exit nodes.  So in our infrastructure, we have:

user agent → Lantern client → CDN → Lantern proxy → destination.

Lantern hosts dozens of such proxies on commodity VPS providers like
Digital Ocean. In addition, uncensored users who run the Lantern client can
register themselves as domain-fronted proxies as well, so overall there are
theoretically a very large number of proxies in rotation at any one time.

\subsection{Choice of CDN}
In our initial implementation, we used Fastly as our CDN.  Fastly ended up
being unsuitable because their infrastructure isn't meant to support a
large number of backends, so we transitioned to CloudFlare.  CloudFlare has
worked well so far because it supports a large number of backends, it has
an API that we can use to manage those backends and it has cheap flat-rate
pricing that doesn't charge based on bandwidth consumption. It also has
a sufficient number of relatively high-profile domains through which we can
front.

\subsection{Implementation Components}
Lantern's domain fronting is implemented in Go and made available through
the flashlight~\cite{flashlight} application.
The core of flashlight's domain fronting is encapsulated in two libraries,
enproxy~\cite{enproxy} and fronted~\cite{fronted}.

enproxy provides an implementation of Go's standard net.Conn interface that
encapsulates reads and writes as a series of HTTP requests via a stateful
enproxy proxy.  This allows flashlight to proxy any streaming-oriented
traffic (e.g. TCP).  Unlike meek, enproxy supports full-duplex~\cite{beating-gfw-with-go} operation
so that reads don't wait on writes, which can be handy for bidirectional
protocols like XMPP.  Lantern actually uses XMPP as a signaling channel for
peer-to-peer traffic, and tunnels XMPP via domain-fronted proxies.

fronted uses domain-fronting to transmit enproxy's HTTP requests in a
blocking-resistant manner. It provides a facility for configuring a number
of different front domains (masquerade hosts) and includes the ability to
connect to them directly by IP address rather than DNS. In practice,
flashlight uses several hundred masquerade hosts when communicating via
CloudFlare.

\subsection{Sticky Routing}
Domain-fronted Lantern requests go to one of two host names,
fallbacks.getiantem.org and peers.getiantem.org.  Fallbacks is a pool of
servers hosted by Lantern, and peers is the pool of servers constituted by
online Lantern peers.  When using CloudFlare, a server is selected based by
round robin.  Just like with meek, Lantern's domain-fronting protocol is
stateful, so subsequent HTTP requests for the same connection need to find
their way back to the same proxy that handled the original request.  We
accomplish this by having the responding proxy return its specific hostname
in a header which the client then users on subsequent requests, thereby
bypassing the round robin.

@@

Firstly, domain-fronting requires the establishment of additional TCP
connections. In a best case scenario, the user agent can open a single TCP
connection directly to the destination server.  With Lantern, the inclusion
of the client, CloudFlare and the proxy introduce three additional TCP
connections between the user agent and the destination.  This is mitigated
somewhat by the fact that CloudFlare pools and reuses connections to the
Lantern proxy.  Unfortunately, the Lantern client cannot do the same for
connections to CloudFlare as CloudFlare seems to time out idle connections
fairly aggressively.  We mitigate this somewhat by aggressively
pre-connecting to CloudFlare when we detect activity~\cite{connpool}.

@@

Thirdly, enproxy does not pipeline http requests.  This means that even
though reads and writes are full duplex, the flush of one set of writes
cannot proceed until the previous flush of the previous set of writes has
been acknowledged with an http response, meaning that a full round-trip is
necessary between each flush. Implementing HTTP 2.0 would provide request
pipelining and potentially improve on latency substantially.

Fourthly, enproxy has no way of knowing when the user agent is done
writing.  If the data were streaming directly from user agent through to
the proxy, this wouldn't be a problem, but CDNs like CloudFlare buffer
uploads fairly aggressively, so small uploads aren't actually forwarded to
the proxy until the HTTP request is finished.  enproxy assumes that a
writer is finished if it detects inactivity for more than 35 milliseconds,
at which point it flushes the write by finishing the HTTP request.  This
introduces at least 35 milliseconds of additional latency, and potentially
more if we guessed wrong and the write wasn't actually finished, since we
now have to wait for a full round trip before the next write can proceed.
This latency is particularly noticeable when proxying TLS traffic, as the
TLS handshake consists of several small messages sent back and forth
between user agent and server.

This fourth source of latency can be eliminated if enproxy can know for
sure when a writer is finished. This could be achieved by changing the
interface so that rather than implementing net.Conn and proxying generic
streams of traffic, enproxy could actually proxy HTTP requests directly. It
would be able to tell when the user agent is finished sending an HTTP
request and when the destination is finished responding.  However, doing
the same for HTTPS would require man-in-the-middling the TLS connection in
order to expose the flow of requests.  Furthermore, this approach only
works for HTTP clients.  Supporting other sorts of traffic like XMPP would
require implementing support for those protocols as well.

\subsection{Buffering versus Streaming Requests and Responses}
HTTP supports both buffered requests/responses (fixed content-length) and
streaming (chunked encoding). For large downloads and uploads in
particular, streaming is attractive because it allows writes to stream
through the proxy and CDN without blocking and as part of a single HTTP
request/response.  Some CDNs support streaming requests and responses, some
support only streaming responses, and some support neither streaming
requests nor responses.  CloudFlare supports streaming in both directions.

enproxy provides pluggable strategies to use either streaming or
buffering.

\subsection{Managing Proxy Rotations}
Lantern hosted proxies are fairly stable, but peer proxies tend to come
online and offline fairly frequently. The CDN (CloudFlare) configuration
needs to be kept up-to-date based on which proxies are available at any
given time. We achieve this using the peerscanner~\cite{peerscanner} application, which
provides a REST API for proxies to register and unregister themselves.
peerscanner does continual connectivity checking of registered proxies and
maintains the CloudFlare configuration accordingly. This process is
unfortunately not foolproof, because there is some latency in the
connectivity checking and some further latency in the updating of
CloudFlare's configuration and the propagation of those updates through
CloudFlare's infrastructure (haven't measured this).  This means that there
will be periods of time during which an offline proxy is still in rotation,
which causes an error for any user that's unlucky enough to get routed to
it.

\subsection{Direct Domain Fronting}
One of our services is a geolocation server. Rather than proxying traffic to it
via our enproxy proxies, we actually have it registered on CloudFlare and
domain-front to it directly.  This reduces latency and saves resources on our
end.  We've talked about doing direct domain-fronting for popular sites by just
registering their IPs in CloudFlare under special domains, for example
\urll{facebook.direct.getiantem.org}.  To do this for anything that's HTTPS would
require us to man-in-the-middle connections from the user agent.  The biggest
problem with man-in-the-middling isn't that our client-side Lantern software
sees the traffic in the clear, it's that the CDN also sees it in the clear.

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-psiphon3}
\caption{
Daily unique users of \meek with
Psiphon.
We don't have user accounts or track users by e.g., IP address. We do
count connection events. The unique user number is derived from a
coarse-grained ``last connected'' timestamp sent by clients: if the last day
connected is before day being counted, then that connected event is a
unique user for that day.
}
\label{fig:clients-psiphon3}
\end{figure}

@@

% [Blinded circumvention tool]
% % ANON
% % Psiphon
% began their independent deployment of \meek in June~2014.
% Figure~\ref{fig:clients-psiphon3} shows the number
% of unique daily users of \meek%
% ,
% % ANON
% % with Psiphon,
% estimated through clients' self-reporting of their most recent connection date.
% The developers tell us that the drop that occurs
% in the middle of June was not caused by a blocking event,
% but rather an unblocking event that made \meek unnecessary for some users.
% Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
% are not directly comparable because they count slightly different things,
% it is clear that meek-with-%
% [blinded circumvention tool],
% % ANON
% % Psiphon,
% with its thousands of daily users,
% is much more widely used than meek-with-Tor, which has not yet seen a formal release.

>>>>

Lantern~\cite{lantern} is a free circumvention tool for casual web browsing.
Lantern does not employ onion routing and focuses more on performance and
availability rather than anonymity.

Lantern encompases a network of shared HTTPS proxy servers along with a client
application that allows censored users to find and use those proxy servers to
proxy traffic for their existing web browsers. The Lantern client also allows
uncensored users to host proxy servers for use by other Lantern users. Lantern 
aims to provide a secure mechanism for distributing knowledge about both
Lantern-hosted and peer-hosted proxy servers using a trust-network based
distribution mechanism such as kaleidoscope~\cite{kaleidoscope}. In the
meantime, Lantern also randomly assigns users to Lantern-hosted proxy servers.

Lantern uses a centralized infrastructure for authenticating users and
assigning proxies to them. Lantern's threat model assumes that this
centralized infrastructure can be blocked by censors. So, users must have a
priori access to an unblocked proxy which they can use to bootstrap onto the
Lantern network. We call these "fallbacks".

Lantern originally distributed the IP addresses of fallbacks by embedding them
in customized software installers that we sent to users via email in response to
a request from the user. This prevented users from directly downloading Lantern
from our website and made it easy for censors to discover proxies simply by
signing up for Lantern (though in practice we never saw this happen).

\subsection{Timeline for Deploying Domain Fronting}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{bandwidth-lantern}
\caption{
Megabytes per second served by domain fronted Lantern proxies
(Lantern-hosted and peers).
}
\label{fig:lantern-bandwidth}
\end{figure}

After initially testing with Fastly, Lantern rolled out domain fronting on
CloudFlare in July 2014, allowing users to direct-download Lantern for the first
time. These direct-downloaded Lantern clients proxied all their traffic via
domain fronting. CloudFlare has proven attractive because 1) it has a sufficient
number of unblocked front domains available in China, 2) it doesn't charge for
bandwidth and 3) it provides an API for registering and unregistering our
proxies.

After experiencing steady growth, in October 2014 we started randomly assigning
direct HTTPS proxies to users who had direct-downloaded Lantern. This diverted
traffic from domain fronted servers to more efficient direct servers.

In December 2014 and January 2015, Lantern experienced a dramatic surge in
domain fronted traffic, jumping from 1 MB/s to 100 MB/s within those two
months, and activity has remained at around the 100 MB/s level since then.

\subsection{Implementation Components}
Lantern's domain fronting is available via the flashlight~\cite{flashlight}
application, which uses the enproxy~\cite{enproxy} and fronted~\cite{fronted}
libraries to implement domain fronting

enproxy provides an implementation of Go's standard net.Conn interface that
encapsulates reads and writes as a series of HTTP requests via a stateful
enproxy proxy. This allows flashlight to proxy any streaming-oriented
traffic (e.g. TCP). Unlike meek, enproxy supports
full-duplex~\cite{beating-gfw-with-go} operation, which can be handy for
bidirectional protocols like XMPP, which Lantern uses for P2P signaling.

fronted uses domain fronting to transmit enproxy's HTTP requests in a
blocking-resistant manner. In practice, we configure fronted with several
hundred host domains dialed via IP (no DNS lookup).

\subsection{Sticky Routing}
Domain fronted Lantern requests go to host names that represent pools of servers
such as fallbacks.getiantem.org. CloudFlare distributes requests to the servers
in round robin. Just like with meek, Lantern's domain-fronting protocol is
stateful, so subsequent HTTP requests for the same connection are routed back to
the original responding proxy using the proxy's specific hostname, which the
client obtains from a custom HTTP header.

@@

Firstly, domain fronting requires the establishment of additional TCP
connections. At best, the user agent can open a single TCP
connection directly to the destination server. With Lantern, the client,
CloudFlare and the proxy introduce three additional TCP connections between the
user agent and the destination. To reduce latency, CloudFlare pools and reuses
connections to the Lantern proxy. Unfortunately, the Lantern client cannot do
the same for connections to CloudFlare because CloudFlare seems to time out
idle connections fairly aggressively. We mitigate this by aggressively
pre-connecting to CloudFlare when we detect activity~\cite{connpool}.

@@

Thirdly, enproxy does not pipeline http requests. So even though reads and
writes are full duplex, the flush of one set of writes cannot proceed until the
flush of the previous set of writes has been acknowledged with an http response,
meaning that a full round-trip is necessary between each flush. Implementing
HTTP 2.0 would provide request pipelining and potentially improve on latency
substantially.

Fourthly, enproxy has no way of knowing when the user agent is done
writing. If the data were streaming directly from user agent through to
the proxy, this wouldn't be a problem, but CDNs like CloudFlare buffer
uploads fairly aggressively and small uploads aren't actually forwarded to
the proxy until the HTTP request is finished. enproxy assumes that a
writer is finished if it detects inactivity for more than 35 milliseconds,
at which point it flushes the write by finishing the HTTP request. This
introduces at least 35 milliseconds of additional latency, and potentially
more if we guessed wrong and the write wasn't actually finished, since we
now have to wait for a full round trip before the next write can proceed.
This latency is particularly noticeable when proxying TLS traffic, as the
TLS handshake consists of several small messages between user agent and server.

This fourth source of latency can be eliminated if enproxy can know for
sure when a writer is finished. This can be achieved by enproxy handle the HTTP
protocol specifically. This would allow enproxy to know when the user agent is
finished sending an HTTP request and when the destination is finished
responding. However, doing the same for HTTPS would require man-in-the-middling
the TLS connection in order to expose the flow of requests. Furthermore, this
approach only works for HTTP clients. Supporting other sorts of traffic like
XMPP would require additional support for those protocols.

\subsection{Direct Domain Fronting}
The Lantern network includes a geolocation server. This server is directly
registered on CloudFlare and the Lantern client domain-fronts directly to the
geolocation server without using any proxies. This reduces latency and saves
proxy resources. This sort of direct domain fronting technique can in theory be
implemented for any HTTP site simply be registering it under a custom domain
such as \urll{facebook.direct.getiantem.org}. This can even be accomplished for
HTTPS but requires the Lantern client to man-in-the-middle connections from the
user agent, exposing the plaintext not only to the Lantern client but also to
CloudFlare. In practice, any sights that use CloudFlare themselves already
expose their plaintext to CloudFlare, so this may be an acceptable solution.

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-psiphon}
\caption{
Daily unique users of \meek with
Psiphon.
We don't have user accounts or track users by e.g., IP address. We do
count connection events. The unique user number is derived from a
coarse-grained ``last connected'' timestamp sent by clients: if the last day
connected is before day being counted, then that connected event is a
unique user for that day.
}
\label{fig:clients-psiphon}
\end{figure}

@@

% [Blinded circumvention tool]
% % ANON
% % Psiphon
% began their independent deployment of \meek in June~2014.
% Figure~\ref{fig:clients-psiphon} shows the number
% of unique daily users of \meek%
% ,
% % ANON
% % with Psiphon,
% estimated through clients' self-reporting of their most recent connection date.
% The developers tell us that the drop that occurs
% in the middle of June was not caused by a blocking event,
% but rather an unblocking event that made \meek unnecessary for some users.
% Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon}
% are not directly comparable because they count slightly different things,
% it is clear that meek-with-%
% [blinded circumvention tool],
% % ANON
% % Psiphon,
% with its thousands of daily users,
% is much more widely used than meek-with-Tor, which has not yet seen a formal release.
